Pillar 1 - Sequential Pattern Mining

### 2019-01-28 Pillar 1 - Sequential Pattern Mining.Rmd
ungroup()

###NOTE for FURTURE: create filter by function
##Create filter condition.
```{r}
string_filter <- case_when(quo_name(category)=="Outcome"        ~ "Fail",
                           quo_name(category)=="Low_grade"      ~ "low score",
                           quo_name(category)=="Discrete_grade" ~ "5",
                           quo_name(category)=="None"           ~ "_" #useless filter
                           )
```
##CSPADE Algorithm:
```{r}
frequent_trajectories <- cspade(transactions, parameter = list(support = 0,
                                                               maxsize = 1,
                                                               maxlen = 2), control   = list(verbose = TRUE))

@@

```{r}

@@

```{r}
n_students <- length(unique(d_sequence_transactions$`Student ID`))

@@

  # Compute statistics
  group_by(LHS,`RHS Course ID`) %>%
  arrange(LHS,`RHS Course ID`)
  mutate(
    Prob_both = sum(support), 
    Conf_corr = support/Prob_both,
    n_rule    = support * n_students,
    n_both    = Prob_both * n_students,
    lift_diff = Conf_corr - Prop_low,
    lift_corr = Conf_corr / Prop_low
    ) %>%
  ungroup() %>%

>>>>

###NOTE for FURTURE: create filter by function
##Create filter condition.
```{r}
string_filter <- case_when(quo_name(category)=="Outcome"        ~ "Fail",
                           quo_name(category)=="Low_grade"      ~ "low score",
                           quo_name(category)=="Discrete_grade" ~ "5",
                           quo_name(category)=="None"           ~ "_" #useless filter
                           )
```
##CSPADE Algorithm:
```{r}
frequent_trajectories <- cspade(sequences, parameter = list(support = 0,
                                                               maxsize = 1,
                                                               maxlen = 2), control   = list(verbose = TRUE))

@@

Excluding manatory courses.
```{r}

@@

```{r}
category
n_students <- length(unique(d_sequence_transactions$`Student ID`))

@@

  # Compute statistics
  group_by(LHS,`RHS Course ID`) %>%
  mutate(
    Prob_both = sum(support))%>%
  ungroup()%>%
  mutate( 
    Conf_corr = support/Prob_both,
    n_rule    = support * n_students,
    n_both    = Prob_both * n_students,
    lift_diff = Conf_corr - Prop_low,
    lift_corr = Conf_corr / Prop_low
    )
